Synthesising Concise Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-07 papers/termination/paper.tex
related

>>>>

\cite{DBLP:journals/entcs/BiereAS02}

\cite{DBLP:conf/sas/HarrisLNR10}
 TREX, a novel algorithm for proving termination of whole programs. TREX
simultaneously maintains over and under-approximations of a loop
to quickly find proofs of termination or non-termination. This allows it to com-
pose several program analyses that until no
w were disparate: termination provers
for multi-path loops, non-termination prove
rs for cycles, and global safety provers.
